An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-04-04 tex/paper.tex
Adding verbatim code highlighting.

\usepackage{amsmath}  % Basic
\usepackage{booktabs}  % Better tables
\usepackage{graphicx}  % Images
\usepackage{hyperref}  % Links etc
\usepackage{minted}  % Code
\usepackage{multicol}  % Multi column list
\usepackage{subcaption}  % Subfigures

@@

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
>>> import axelrod
>>> strategies = [s() for s in axelrod.demo_strategies]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()
    \end{minted}
    \caption{A simple set of commands to create a demonstration tournament. The
        output is shown in Figure~\ref{fig:demo_tournament}.}
    \label{fig:demo_tournament_commands}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
class Grudger(Player):
    """A player starts by cooperating however will defect if
       at any point the opponent has defected."""

@@

    def strategy(self, opponent):
        """Begins by playing C, then plays D for the remaining
           rounds if the opponent ever plays D."""
        if opponent.defections:
            return D
        return C
    \end{minted}
    \caption{Source code for the Grudger strategy.}
    \label{fig:grudger}
\end{figure}

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
class TestGrudger(TestPlayer):

@@

    def test_strategy(self):
        """
        If opponent defects at any point then the player will defect forever
        """
        self.responses_test([C, D, D, D], [C, C, C, C], [C])
        self.responses_test([C, C, D, D, D], [C, D, C, C, C], [D])
    \end{minted}
    \caption{Test code for the Grudger strategy.}
    \label{fig:grudger_test}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
>>> import axelrod

>>> strategies = [axelrod.Cooperator(),
...               axelrod.Defector(),
...               axelrod.ZDExtort2(),
...               axelrod.Joss(),
...               axelrod.HardTitForTat(),
...               axelrod.HardTitFor2Tats(),
...               axelrod.TitForTat(),
...               axelrod.Grudger(),
...               axelrod.TitFor2Tats(),
...               axelrod.WinStayLoseShift(),
...               axelrod.Random(),
...               axelrod.ZDGTFT2(),
...               axelrod.GTFT(),
...               axelrod.HardProber(),
...               axelrod.Prober(),
...               axelrod.Prober2(),
...               axelrod.Prober3(),
...               axelrod.Calculator(),
...               axelrod.HardGoByMajority()]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()
    \end{minted}
    \caption{Source code for reproducing the tournament of \cite{Stewart2012}}
    \label{fig:stewart-code}
\end{figure}

>>>>

\usepackage{amsmath}  % Basic
\usepackage{booktabs}  % Better tables
\usepackage{graphicx}  % Images
\usepackage{hyperref}  % Links etc
% \usepackage{minted}  % Code: minted does not compile on arXiv
\usepackage{multicol}  % Multi column list
\usepackage{subcaption}  % Subfigures

@@

\begin{figure}[!hbtp]
    \begin{verbatim}
>>> import axelrod
>>> strategies = [s() for s in axelrod.demo_strategies]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()
    \end{verbatim}
    \caption{A simple set of commands to create a demonstration tournament. The
        output is shown in Figure~\ref{fig:demo_tournament}.}
    \label{fig:demo_tournament_commands}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{verbatim}
class Grudger(Player):
    """A player starts by cooperating however will defect if
       at any point the opponent has defected."""

@@

    def strategy(self, opponent):
        """Begins by playing C, then plays D for the remaining
           rounds if the opponent ever plays D."""
        if opponent.defections:
            return D
        return C
    \end{verbatim}
    \caption{Source code for the Grudger strategy.}
    \label{fig:grudger}
\end{figure}

\begin{figure}[!hbtp]
    \begin{verbatim}
class TestGrudger(TestPlayer):

@@

    def test_strategy(self):
        """
        If opponent defects at any point then the player will defect forever
        """
        self.responses_test([C, D, D, D], [C, C, C, C], [C])
        self.responses_test([C, C, D, D, D], [C, D, C, C, C], [D])
    \end{verbatim}
    \caption{Test code for the Grudger strategy.}
    \label{fig:grudger_test}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{verbatim}
>>> import axelrod

>>> strategies = [axelrod.Cooperator(),
...               axelrod.Defector(),
...               axelrod.ZDExtort2(),
...               axelrod.Joss(),
...               axelrod.HardTitForTat(),
...               axelrod.HardTitFor2Tats(),
...               axelrod.TitForTat(),
...               axelrod.Grudger(),
...               axelrod.TitFor2Tats(),
...               axelrod.WinStayLoseShift(),
...               axelrod.Random(),
...               axelrod.ZDGTFT2(),
...               axelrod.GTFT(),
...               axelrod.HardProber(),
...               axelrod.Prober(),
...               axelrod.Prober2(),
...               axelrod.Prober3(),
...               axelrod.Calculator(),
...               axelrod.HardGoByMajority()]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()
    \end{verbatim}
    \caption{Source code for reproducing the tournament of \cite{Stewart2012}}
    \label{fig:stewart-code}
\end{figure}
